Group polarization replications may be marred by high false discovery rates

### 2025-01-25 GroupPolarizationStatmod/paper/ms.tex
nearly done with Analysis
fixed up table in final push for final draft

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=gray}
\setcounter{tocdepth}{3}
\tableofcontents
}

@@

To calculate the false detection rate we begin by simulating 
pre- and post-deliberation 
opinions by drawing $N_e$ samples from normal latent opinion
distributions that generated spurious group polarization, i.e., with
parameters labelled $\beta_e$ found in the hillclimbing step. Binning these
random values simulates observations. $N_e$ is the number
of participants in experimental condition $e$. Each trial $i$ of $N_e$
simulated pre- and post-deliberation observations is then inspected to see
if spurious group polarization occurred in the simulation. Spurious group
polarization is determined by first inferring the latent parameters of each
simulated experimental trial by fitting an ordered probit model~\cite{Liddell2018}. 
The inferred parameters are then used to calculate the effect size for that
trial, Cohen's $d$, defined as~\cite[p. 331]{Liddell2018}
\begin{equation}
  d = \frac{\mupost - \mupre}{\sqrt{\frac{1}{2}(\sigmapost^2 + \sigmapre^2)}}.
  \label{eq:cohens}
\end{equation}
\noindent
The family-wise error rate is, $\alpha_{e} = \Pr(D|\neg E)$, is the 
fraction of trials, 
with $d_{ei} > d^*$ for the $i^\text{th}$ trial for experimental
condition $e$, written
\begin{equation}
  \alpha_e = \frac{1}{N_T} \sum_i^{N_T} \Theta(d_{ei}; d^*),
  \label{eq:study_aggregate}
\end{equation}
\noindent
where
\[
  \Theta(d_{ei}; d^*) = 
    \begin{cases}
      1 & \text{ if } d_{ei} > d^* \\
      0 & \text{ otherwise.}
    \end{cases}
\]
and $N_T = 1000$ is the number of trials. For simplicity we assume that the sign of
$d_{ei}$ is positive, meaning a shift to greater extremisim. It is possible that
$d_{ei}$ could be negative, indicating a shift to lesser extremity.

@@

\begin{table}[ht]
  \caption{{\textbf{Quantiles for the two error-rate measures under different
  significance values.}\mt{Working on splitting in two and having more base rate
and power conditions.}}}
  \label{tab:quantiles}
\rotatebox{90} {
  \input{tex/quantile_table.tex}
}
\end{table}

@@

\subsection{Minimum $d^*$ for FWER of 0.05}

Solving the inverse problem of which $d^*$ achieves a low family-wise error rate,
which drives the false detection rate. Here we present our calculations to find
$d^*$ that achieve $\alpha(d^*) = 0.05$.

@@

%%%%%%%%%% Supplement %%%%%%%%%%
\pagebreak
\begin{center}
  \textbf{\Large \textsf{Minority-group incubators and majority-group
reservoirs support the diffusion of climate change adaptations (Supplementary Material)}}
\end{center}

>>>>

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=gray}
\setcounter{tocdepth}{2}
\tableofcontents
}

@@

To calculate the false detection rate we begin by simulating 
pre- and post-deliberation 
opinions by drawing $N_e$ samples from normal latent opinion
distributions that generated spurious group polarization, i.e., with
parameters labelled $\beta_e$ found in the hillclimbing step. Binning these
random values simulates observations. $N_e$ is the number
of participants in experimental condition $e$. Each trial $i$ of $N_e$
simulated pre- and post-deliberation observations is then inspected to see
if spurious group polarization occurred in the simulation. Spurious group
polarization is determined by first inferring the latent parameters of each
simulated experimental trial by fitting an ordered probit model~\cite{Liddell2018}. 
The inferred parameters are then used to calculate the effect size for that
trial, Cohen's $d$, defined as~\cite[p. 331]{Liddell2018}
\begin{equation}
  d = \frac{\mupost - \mupre}{\sqrt{\frac{1}{2}(\sigmapost^2 + \sigmapre^2)}}.
  \label{eq:cohens}
\end{equation}
\noindent
The family-wise error rate is, $\alpha_{e} = \Pr(D|\neg E)$, is the 
fraction of trials, 
with $d_{ei} > d^*$ for the $i^\text{th}$ trial for experimental
condition $e$, written
\begin{equation}
  \alpha_e = \frac{1}{N_T} \sum_i^{N_T} \Theta(d_{ei}; d^*),
  \label{eq:study_aggregate}
\end{equation}
\noindent
where
\[
  \Theta(d_{ei}; d^*) = 
    \begin{cases}
      1 & \text{ if } d_{ei} > d^* \\
      0 & \text{ otherwise.}
    \end{cases}
\]
and $N_T = 1000$ is the number of trials. For simplicity we assume that the sign of
$d_{ei}$ is positive, meaning a shift to greater extremisim. It is possible that
$d_{ei}$ could be negative, indicating a shift to lesser extremity. Indeed we
observe many simulations with a shift to lesser extremity. For now we do not
include these as indicating a ``significant'' effect, which we return to in the
Analysis below.

@@

\begin{table}[ht]
  \caption{{\textbf{Quantiles for the two error-rate measures under different
  significance values.}}}
  \label{tab:quantiles}
  \centering
  \input{tex/quantile_table_min_20_50_80_max.tex}
\end{table}

@@

\subsection{High significance values ($d^*$) often necessary for FWER of 0.05}

Our simulations can be used a different way, in this case to calculate what
significance value $d^*$ limits the family-wise error rate to the low value of
0.05. 
Solving the inverse problem of which $d^*$ achieves a low family-wise error rate,
which drives the false detection rate. Here we present our calculations to find
$d^*$ that achieve $\alpha(d^*) = 0.05$.

@@

%%%%%%%%%% Supplement %%%%%%%%%%
\pagebreak
\begin{center}
  \textbf{\Large \textsf{Group polarization replications may be marred by high false discovery rates (Supplementary Material)}}
\end{center}
